---
output: github_document
---

```{r, echo = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "README-"
)
```

# `spcrimr`: tidy data from Secretaria de Segurança Pública - São Paulo, Brazil

`spcrimr` is a simple package to download and use tidy data from Secretaria de Sweegurança Pública, state of Sao Paulo, Brazil.

With this package you can easily download tables from [SSP's website](http://www.ssp.sp.gov.br/Estatistica/Pesquisa.aspx).

The `download_table_sp()` function request tables from [SSP's website](http://www.ssp.sp.gov.br/Estatistica/Pesquisa.aspx) with `R` and displays it in the conlose.


## Installation

You can install `spcrimr` from github with:

```{r gh-installation, eval = FALSE}
# install.packages("devtools")
devtools::install_github("rdurl0/spcrimr")
```

## Example

### Data

```{r}
library(spcrimr)
library(tibble)

glimpse(ssp_ocorrencias_crimes)

glimpse(ssp_produtividade_policial)

glimpse(ssp_variables_names)

glimpse(seade) # a database from SEADE
```

### Functions

The `download_table_sp` function download tables from [SSP's website](http://www.ssp.sp.gov.br/Estatistica/Pesquisa.aspx)

```{r}
download_table_sp(ano = 2019,
                  municipio = 500,
                  type = "ctl00$conteudo$btnMensal") %>% glimpse()
```


```{r}
insert_munic_idx("any vector") %>% glimpse()
```


## Citation

To cite `spcrimr`, write `citation("spcrimr")`:

```
To cite package ‘spcrimr’ in publications use:

  Raul de Sá Durlo (2019). spcrimr: tidy data from SSP-SP.
  R package version 0.0.9000.

A BibTeX entry for LaTeX users is

  @Manual{,
    title = {spcrimr: tidy data from SSP-SP},
    author = {Raul de Sá Durlo},
    year = {2019},
    note = {R package version 0.0.9000},
  }
```
